Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2023-01-03 response_to_reviewers_R1.Rmd

> Thank you for your feedback.

- If there is still space allowed in the abstract, I think you could consider explicitly
mentioning the three big ideas (expected value of a game state, win probability, and
measures of team strength). This would give readers a better idea of what is to come
and also allow people to find your article more easily if they are interested in one of
those specific topics.

> Thank you for this suggestion. We have added the three ideas explicitly to the abstract.

- In Section 2.1.2, I am a little confused as to what Carroll et. al. did to extend the
previous model of Carter and Machol, since both efforts seem to involve some sort of
linearity assumption.
- Also in Section 2.1.2, it might be worthwhile to briefly define absorbing states, as I for
one didn’t know the definition before looking it up (and as it turns out the concept is
quite simple)

> We have added a sentence defining what an absorbing state is: "An absorbing state is a link in a Markov chain from which there are no possible transitions (i.e., it is the end of the chain)."

- In Section 2.1.3, you make the comment “they estimate that a better strategy would
be worth about 0.4 wins per season on average, a substantial amount in a season with
only 16 games.” This makes sense, but previously in Section 2.1.2 you mentioned
a potential difference of 3.8 wins per season, yet didn’t comment on the significant
magnitude of that effect. I’m not advocating for a particular change here, but the
authors could consider adding a small comment about the size of the effect Pelechrinis
et. al. estimated.
- At the end of Section 2.1.3, you write “Lopez (2020) also concludes that coaches are
too conservative on 4th down decision making, but the effect may be overstated due
to the way in which to go yardage has been recorded in the past.” It’s unclear to me
whether the overstated effect is the one Lopez estimates in his paper, or if you are
referring to the estimated effects past studies which used less granular data.
- In Section 2.3, you write “NHL coaches do not always employ the optimal strategies”,
but it isn’t clear what those strategies are in reference to the previous discussion. Is
pulling the goalie optimal?
- In the second formula of Section 4.1, the right hand side of the equation has a 2, but
it should be an α.

### 2023-01-03 sports_analytics.Rmd
defined absorbing state; #43

[^state]: 25, if you include the absorbing state of 3 outs.

@@

Other attempts at modeling expected points in football are @goldner2012markov and @goldner2017situational, who propose a Markov framework.
In particular, the author considers a football drive as an *absorbing Markov chain*, consisting of distinct *absorbing states* that include touchdowns, field goals, and other play outcomes. 
For any given play, the expected points are calculated using the absorption probabilities for different scoring events.

>>>>

[^state]: 25, if you include the absorbing state of 3 outs that describes the end of an inning.

@@

Other attempts at modeling expected points in football are @goldner2012markov and @goldner2017situational, who propose a Markov framework.
In particular, the author considers a football drive as an *absorbing Markov chain*, consisting of distinct *absorbing states* that include touchdowns, field goals, and other possession outcomes. 
An absorbing state is a link in a Markov chain from which there are no possible transitions (i.e., it is the end of the chain).
For any given play, the expected points are calculated using the absorption probabilities for different scoring events.
